Validated Model Counting Data \\ Version of \today

### 2023-02-19 doc/mc-data.tex
Improve data gathering

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=1000000000, 
                              x post scale=2.0, y post scale=2.0,
                              xmin=0,xmax=900,
                              xtick = {0,100,200,300,400,500,600,700,800,900},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$},
                              xlabel={D4 runtime}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining}
          \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4}
\end{figure}

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=1000000000, 
                              x post scale=2.0, y post scale=2.0,
                              xmode=log, xmin=001,xmax=1000,
                              xtick={0.01, 0.1,1.0,10,100,1000}, xticklabels={0.01, 0.1, 1.0, 10, 100, 1000},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$},
                              xlabel={D4 runtime}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining}
          \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4:log}
\end{figure}

@@

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=0.01, ymax=10000,
                              x post scale=2.0, y post scale=2.2,
                              xmode=log,xmin=0.01,xmax=1000,
                              xtick={0.01, 0.1,1.0,10,100,1000}, xticklabels={0.01, 0.1, 1.0, 10, 100, 1000},
                              ytick={0.01, 0.1,1.0,10,100,1000,10000}, yticklabels={0.01, 0.1, 1.0, 10, 100, 1000,10000},
                              xlabel={D4 runtime}, ylabel={CRAT generation runtime},
%                              title={D4 Defining Clause Generation}
            ]
    \addplot[mark=none, color=darkestblue] coordinates{(0.01,0.01) (1000.0,1000.0)};
    \addplot[mark=none, color=midblue] coordinates{(0.01,0.1) (1000,10000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,1.0) (100,10000)};
    \input{data-formatted/time-d4-gen}
    \node[left] at (axis cs: 0.09,0.12) {$1{}.0\times$};
    \node[left] at (axis cs: 0.09,1.2) {$10\times$};
    \node[left] at (axis cs: 0.09,12.0) {$100\times$};

          \end{axis}
\end{tikzpicture}
} % centering
\caption{Runtime for CRAT proof generation as function of D4 runtime}
\label{fig:d4:crat}

>>>>

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=1000000000, 
                              x post scale=2.0, y post scale=2.0,
                              xmin=0,xmax=1000,
                              xtick = {0,100,200,300,400,500,600,700,800,900,1000},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$},
                              xlabel={D4 runtime (seconds)}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining-success}
    \input{data-formatted/time+defining-failure}
          \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4}
\end{figure}

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=1000000000, 
                              x post scale=2.0, y post scale=2.0,
                              xmode=log, xmin=001,xmax=1000,
                              xtick={0.01, 0.1,1.0,10,100,1000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$},
                              xlabel={D4 runtime (seconds)}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining-success}
    \input{data-formatted/time+defining-failure}
          \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4:log}
\end{figure}

@@

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=0.01, ymax=20000,
                              x post scale=2.0, y post scale=2.2,
                              xmode=log,xmin=0.01,xmax=1000,
                              xtick={0.01, 0.1,1.0,10,100,1000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}},
                              ytick={0.01, 0.1,1.0,10,100,1000,10000,20000}, yticklabels={0.01, 0.1, 1.0, 10, 100, {1,000},{10,000},{20,000}},
                              xlabel={D4 runtime (seconds)}, ylabel={CRAT generation and checking runtime (seconds)},
%                              title={D4 Defining Clause Generation}
            ]
    \addplot[mark=none, color=darkestblue] coordinates{(0.01,0.01) (1000.0,1000.0)};
    \addplot[mark=none, color=midblue] coordinates{(0.01,0.1) (1000,10000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,1.0) (200,20000)};
    \input{data-formatted/time-d4-verify}
    \node[left] at (axis cs: 0.09,0.12) {$1{}.0\times$};
    \node[left] at (axis cs: 0.09,1.2) {$10\times$};
    \node[left] at (axis cs: 0.09,12.0) {$100\times$};

          \end{axis}
\end{tikzpicture}
} % centering
\caption{Combined runtime for CRAT proof generation and checking  as function of D4 runtime}
\label{fig:d4:crat}
